Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@

@@

Library catalogs contain rich metadata on...

Here we analyse Fennica & Kungliga..

We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).

In summary, the data analytical ecosystem does ..

Reading, parsing, cleaning up, enriching, summarizing, analysis, visualization, figures and tables..

Full source code to reproduce these analyses are available via Github ([Fennica](https://github.com/rOpenGov/fennica/); [Kungliga](https://github.com/rOpenGov/kungliga/)).

>>>>

Paper consumption in selected places (Fennica):

@@

Library catalogues contain rich metadata on...

Here we have analysed Fennica & Kungliga..

@@

We obtained Fennica and Kungliga library catalogues from..

After initial preprocessing, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents in Fennica and Kungliga, respectively between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`.

We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)). In summary, the data analytical ecosystem does .. Reading, parsing, cleaning up, enriching, summarizing, analysis, visualization, figures and tables.. [SUMMARY FIGURE OF THE PROCESS?]. Full source code to reproduce these analyses are available via Github ([Fennica](https://github.com/rOpenGov/fennica/); [Kungliga](https://github.com/rOpenGov/kungliga/)).

A brief summary of the data processing steps:

**Author names**

**Author life years**

**Publication place**

**Publishers**

**Dissertations**

**Duplicate removal** Combining the catalogs ..

**Enriching** to add gender, country, geocoordinates ..
